Conditional 3D Environment Generation Using Deep Adversarial Networks

### 2019-12-06 writing/paper/paper.tex
Write

\title{WorldGAN: 3D Environment Generation Using Deep Adversarial Networks}

@@

@@

@@

>>>>

\title{Conditional 3D Environment Generation Using Deep Adversarial Networks}

@@

	Pix2Pix introduces a a generalized approach to image to image translation problems.  Their model learns not only a mapping between input and output images, but it also learns a loss function between the two image datasets. This allows this model to be used for a variety of image tasks that would originally need very different model and loss configurations \cite{isola2016imagetoimage}.

@@

	CycleGAN introduces the idea of cycle consistency loss. It works by measuring the loss of a mapping from one distribution to another and then back to the original distribution again. This approach allows for good generalization and the advantage of not needing specifically paired images in the training distributions. This can save a lot of time in building large datasets, but it can lose out on the specificity offered by Pix2Pix \cite{zhu2017unpaired}.

@@

	Both models are built on top of the PyTorch framework \cite{paszke2019pytorch}.
